Work Stress

### 2023-03-15 outputs/paper/paper.qmd
upload graph

```{r setup, include = FALSE}
#Load libraries
library(gridExtra)
library(cdlTools)
library(RGraphics)
library(tidyverse)
library(palmerpenguins)
library(knitr)
library(ggplot2)
library(haven)
library(dplyr)
options(dplyr.summarise.inform = FALSE)
```

@@

Most of the figures show lots of visualization of the data. We can easily expect that the birth rate is declining over time within the United States due to many other factors impacting people's decision to have more kids. When it comes to race, there are a lot of data showing some useful information to visualize. Overall, black people tend to have lower birth rates than Hispanic and white people. Hispanics have the highest birth rates, while people are the second highest. But all races are showing a down trendline that the birth rates are going down over time which can be coming from other factors. When it comes to factors like childcare expenses, it shows that people with lower expense tends to have low birth rates, while more expense tends to have more birth rates. When the rental housing costs are high, the number of birth rates tends to go down, and the same for the situation in student loan debt. When it comes to the figures of different races, we decided to focus on age groups such as 15-19 and 20-24 because we believe that this age category has more useful information since we know that in the past, people tended to have kids much earlier than before due to having marriage at an early age. The birth rates by different races in the age group 15-19 have drastically decreased over time when compared to the age group 20-24. This is because fewer people are getting married before age 20 and having kids before age 20.

>>>>

```{r setup, include = FALSE}
#Load libraries
library(dplyr)
library(tidyverse)
library(readxl)
options(dplyr.summarise.inform = FALSE)
```

@@

```{r setup}
#| echo: false
#| message: false
#| label: fig-1
#| fig-cap: Work Stress by Job Status
#Load libraries
raw_data <- read_excel(here::here("inputs/data/GSS.xlsx"))
clean_data <- raw_data %>% 
  select(wrkstat, stress) %>% 
  filter(str_detect(stress, "Always|Often|Sometimes|Hardly ever|Never"),
         str_detect(wrkstat, "Working full time|Working part time"))

positions <- c("Never", "Hardly ever", "Sometimes", "Often", "Always")

clean_data %>% 
  ggplot(aes(group = wrkstat)) +
  geom_bar(aes(x=stress, y = ..prop.., fill=factor(..x..)))+
  labs(y = "Percent", fill="Work Stress", x = 'Work Stress', title = "Work Stress by status" ) +
  facet_wrap(~wrkstat) +
  scale_x_discrete(limits = positions) +
  scale_y_continuous(labels = scales::percent) +
  theme_minimal(base_size = 8) +
  theme(legend.position="none")
```

```{r}
#| echo: false
#| message: false
#| label: fig-2
#| fig-cap: Work Stress by Work Hours
raw_data <- read_excel(here::here("inputs/data/GSS.xlsx"))
clean_data <- raw_data %>% 
  select(hrs1, stress) %>% 
  filter(!str_detect(hrs1, ".i|.y|.n|.d"), str_detect(stress, "Always|Often|Sometimes|Hardly ever|Never"))

clean_data <- clean_data %>% 
  mutate(range = case_when(
    hrs1 < 20 ~ '< 20',
    hrs1 >= 20 & hrs1 < 30 ~ '20-29',
    hrs1 >= 30 & hrs1 < 40 ~ '30-39',
    hrs1 >= 40 & hrs1 < 50 ~ '40-49',
    hrs1 >= 50 & hrs1 < 60 ~ '50-59',
    hrs1 >= 60 ~ '60 over'
  ))

positions <- c("Never", "Hardly ever", "Sometimes", "Often", "Always")

clean_data %>% 
  ggplot() +
  geom_bar(aes(x = stress,  y = ..prop.., group = range, fill=factor(..x..))) +
  scale_x_discrete(limits = positions) +
  scale_y_continuous(labels = scales::percent) +
  facet_wrap(~range) +
  theme_minimal(base_size = 6) +
  theme(legend.position="none")
```

```{r}
#| echo: false
#| label: fig-3
#| fig-cap: Work Stress by Industry Sector
raw_data <- read_excel(here::here("inputs/data/GSS.xlsx"))
clean_data <- raw_data %>% 
  select(wrkgovt, stress) %>% 
  filter(str_detect(wrkgovt, "Government|Private"),
         str_detect(stress, "Always|Often|Sometimes|Hardly ever|Never"))

positions <- c("Never", "Hardly ever", "Sometimes", "Often", "Always")

clean_data %>% 
  ggplot() +
  geom_bar(aes(x = stress,  y = ..prop.., group = wrkgovt, fill=factor(..x..))) +
  scale_x_discrete(limits = positions) +
  scale_y_continuous(labels = scales::percent) +
  facet_wrap(~wrkgovt) +
  theme_minimal(base_size = 8) +
  theme(legend.position="none")
```

```{r}
#| echo: false
#| label: fig-4
#| fig-cap: Work Stress by Job Satisfaction
raw_data <- read_excel(here::here("inputs/data/GSS.xlsx"))
clean_data <- raw_data %>% 
  select(satjob, stress) %>% 
  filter(str_detect(satjob, "Very satisfied|Moderately satisfied|A little dissatisfied|Very dissatisfied"),
         str_detect(stress, "Always|Often|Sometimes|Hardly ever|Never"))

positions <- c("Never", "Hardly ever", "Sometimes", "Often", "Always")

clean_data %>% 
  ggplot() +
  geom_bar(aes(x = stress,  y = ..prop.., group = satjob, fill=factor(..x..))) +
  scale_x_discrete(limits = positions) +
  scale_y_continuous(labels = scales::percent) +
  facet_wrap(~satjob) +
  theme_minimal(base_size = 6) +
  theme(legend.position="none")
```
